---
title: "SC3 package analysis part2"
output: 
  md_document:
    variant: markdown_github
---

Run Seurat analysis to cluster the grafting data, split the before and after grafting cells into separate analyses. 

### Load packages
```{r warnings=FALSE}
suppressMessages(library(Seurat))
suppressMessages(library(gridExtra))
```

### Read data 

```{r}
# read rpkm values
R <-read.table("../data/ensembl_rpkms_filtered.csv", sep=",", header=T)

# read in meta data table
M <- read.table("../data/metadata_all_filtered.csv", sep=",",header=T)

```



# Run Seurat for after grafting

Use Seurat to extract variable genes and scale data by gene detection. 

```{r}
after <- grep("after",M$plate)

savefile<-"../data/seurat_object_after.Rdata"
if(file.exists(savefile)){
  load(savefile)
}else{

  
  dataS <- CreateSeuratObject(raw.data = R[,after], min.cells = 3, min.genes = 200, 
    project = "after_grafting",is.expr=1,meta.data=M[after,])

  scale.factor <- mean(colSums(R[,after]))
  dataS <- NormalizeData(object = dataS, normalization.method = "LogNormalize", 
    scale.factor = scale.factor)

  # variable genes
  dataS <- FindVariableGenes(object = dataS, mean.function = ExpMean, dispersion.function = LogVMR, x.low.cutoff = 1, x.high.cutoff = 10, y.cutoff = 1,cex.text.use=0.2)

  length(x = dataS@var.genes)

  # regress out number of detected genes.d
  dataS <- ScaleData(object = dataS, vars.to.regress = c("nGene"),display.progress=F)

  #PCA
  dataS <- RunPCA(object = dataS, pc.genes = dataS@var.genes, do.print = FALSE)

  #Determine statistically significant principal components
  dataS <- JackStraw(object = dataS, num.replicate = 100, do.print = FALSE)
  JackStrawPlot(object = dataS, PCs = 1:20)


  # select PCs based on JackStraw - all first 12 look fine.
  use.pcs <- 1:12
  dataS <- FindClusters(object = dataS, reduction.type = "pca", dims.use = use.pcs, 
    resolution = 0.6, print.output = 0, save.SNN = TRUE)

  #tSNE

  dataS <- RunTSNE(object = dataS, dims.use = use.pcs, do.fast = TRUE)
  save(dataS,file=savefile)

}

# plot tSNE, define color scale
TSNEPlot(object = dataS,do.label = T, colors.use = c("deepskyblue","blue2","green4","green1","greenyellow","red1","magenta"))

# also plot by cell origin
TSNEPlot(object = dataS, group.by = "sample_type", colors.use = c("red", "blue"))

```


# Run Seurat for before grafting 

```{r}
before <- grep("before",M$plate)

savefile<-"../data/seurat_object_before.Rdata"
if(file.exists(savefile)){
  load(savefile)
}else{

  
  dataSA <- CreateSeuratObject(raw.data = R[,before], min.cells = 3, min.genes = 200, 
    project = "after_grafting",is.expr=1,meta.data=M[before,])

  scale.factor <- mean(colSums(R[,before]))
  dataSA <- NormalizeData(object = dataSA, normalization.method = "LogNormalize", 
    scale.factor = scale.factor)

  # variable genes
  dataSA <- FindVariableGenes(object = dataSA, mean.function = ExpMean, dispersion.function = LogVMR, x.low.cutoff = 1, x.high.cutoff = 10, y.cutoff = 1,cex.text.use=0.2)

  length(x = dataSA@var.genes)

  # regress out number of detected genes.d
  dataSA <- ScaleData(object = dataSA, vars.to.regress = c("nGene"),display.progress=F)

  #PCA
  dataSA <- RunPCA(object = dataSA, pc.genes = dataSA@var.genes, do.print = FALSE)

  #Determine statistically significant principal components
  dataSA <- JackStraw(object = dataSA, num.replicate = 100, do.print = FALSE)
  JackStrawPlot(object = dataSA, PCs = 1:20)


  # select PCs based on JackStraw - skip pc 7 & pc9
  use.pcs <- c(1:6,8,10:12)
  dataSA <- FindClusters(object = dataSA, reduction.type = "pca", dims.use = use.pcs, 
    resolution = 0.6, print.output = 0, save.SNN = TRUE)

#tSNE
  dataSA <- RunTSNE(object = dataSA, dims.use = use.pcs, do.fast = TRUE)
  save(dataSA,file=savefile)
}
# by seurat cluster, define color scale
TSNEPlot(object = dataSA,do.label = T, colors.use = c("green","orange","cyan","yellow2","green4"))
# by plate
TSNEPlot(object = dataSA, group.by = "sample_type", colors.use = c( "hotpink1","grey56"))

```


### Plot some known markers onto the clusters after grafting

```{r}
plotG <- c("OLIG1:ENSG00000184221","GFAP:ENSG00000131095","TH:ENSG00000180176","SLC6A3:ENSG00000142319","GAD2:ENSG00000136750","NXPH4:ENSG00000182379","ALDH1A1:ENSG00000165092","NRSN2:ENSG00000125841","PITX3:ENSG00000107859")

FeaturePlot(object = dataS, features.plot = plotG, cols.use = c("green","yellow","red"), reduction.use = "tsne")
```

# Manually merge clusters

For the after grafting clusters

```{r merge_after}

clusterdef <- c("AC","AC","FBLC","FBLC","FBLC","N","OL")
names(clusterdef) <- as.character(0:6)
merged.clustersA <- clusterdef[as.character(dataS@ident)]

dataS@meta.data$merged.clust <- merged.clustersA

TSNEPlot(dataS, group.by = "merged.clust", colors.use = c("blue1", "green3", "yellow2", "red1"))

```

For before grafting clusters

```{r}
clusterdef <- c("VPE","NPc","VPEP","NPg","VPE")
names(clusterdef) <- as.character(0:4)
merged.clustersB <- clusterdef[as.character(dataSA@ident)]
dataSA@meta.data$merged.clust <- merged.clustersB

TSNEPlot(dataSA, group.by = "merged.clust", colors.use = c("orange", "magenta", "green", "cyan"))

```

### Make one metadata table

Add in the clustering info and write to a file.

```{r}

M$SeuratCluster <- rep("na",nrow(M))
M$SeuratCluster[after] <- paste("Graft-",as.character(dataS@ident),sep="")
M$SeuratCluster[before] <- paste("Culture-",as.character(dataSA@ident), sep="")  
  

M$MergeClust <- rep("na",nrow(M))
M$MergeClust[before]<-merged.clustersB
M$MergeClust[after]<-merged.clustersA

write.table(M, file="../data/meta_data_with_clust.csv",sep=",",quote=F)
```

# Cell cycle scoring

```{r}
# load cell cycle genes
data(cc.genes)

# obs! genes only have gene symbol, in matrix we have gene name + EnsID
rn <- rownames(dataSA@raw.data)
gname <- unlist(lapply(strsplit(rn,":"), function(x) x[1]))
cc.genes <- lapply(lapply(cc.genes, match, gname), function(x) na.omit(rn[x]))
# one gene has no translation, MLF1IP, in our annotation has name CENPU
cc.genes$s.genes <- c(cc.genes$s.genes, rn[grep("CENPU", rn)])


dataSA <- CellCycleScoring(dataSA, g2m.genes = cc.genes$g2m.genes,
                          s.genes = cc.genes$s.genes)

table(dataSA@meta.data$Phase)
TSNEPlot(object = dataSA, group.by = "Phase", do.return=T)
FeaturePlot(dataSA, features.plot = c("S.Score","G2M.Score"), no.legend = F)

dataS <- CellCycleScoring(dataS, g2m.genes = cc.genes$g2m.genes,
                          s.genes = cc.genes$s.genes)

table(dataS@meta.data$Phase)
TSNEPlot(object = dataS, group.by = "Phase", do.return=T)
FeaturePlot(dataS, features.plot = c("S.Score","G2M.Score"), no.legend = F)

```

Clearly, the phase predictions are off for the after cells, where most cells are not cycling. 

### Classify cells as cycling/non-cycling. 

```{r}
cutoff <- 1

cycling <- rep("no", length(dataSA@ident))
cycling[dataSA@meta.data$S.Score > cutoff] <- "yes"
cycling[dataSA@meta.data$G2M.Score > cutoff] <- "yes"
table(cycling)
dataSA@meta.data$cycling <- factor(cycling)

plot(dataSA@meta.data$S.Score, dataSA@meta.data$G2M.Score, col = dataSA@meta.data$cycling,pch=16, ylab="G2M.Score", xlab="S.Score")
TSNEPlot(dataSA, group.by = "cycling")

# same for after
cycling <- rep("no", length(dataS@ident))
cycling[dataS@meta.data$S.Score > cutoff] <- "yes"
cycling[dataS@meta.data$G2M.Score > cutoff] <- "yes"
table(cycling)
dataS@meta.data$cycling <- factor(cycling)

plot(dataS@meta.data$S.Score, dataS@meta.data$G2M.Score, col = dataS@meta.data$cycling, pch=16, ylab="G2M.Score", xlab="S.Score")
TSNEPlot(dataS, group.by = "cycling")
```


#### Plot as pdf

```{r}

f1 <- FeaturePlot(dataS, features.plot = c("S.Score", "G2M.Score"),no.legend = F, do.return = T, no.axes = T)
f1$c1 <- TSNEPlot(dataS, group.by = "cycling", do.return = T, no.axes =T)

f4 <- FeaturePlot(dataSA, features.plot = c("S.Score","G2M.Score"),no.legend = F, do.return = T, no.axes = T)
f4$c2 <- TSNEPlot(dataSA, group.by = "cycling", do.return =T, no.axes =T)

f <- append(f1,f4)
grid.arrange(grobs = f,ncol = 3)


pdf("../data/cell_cycle_scores.pdf", width = 10, height = 7)
grid.arrange(grobs = f,ncol = 3)
dev.off()
```


```{r}
sessionInfo()
````
