---
title: "Seurat_before_grafting_CCregression"
output:
  md_document:
    variant: markdown_github
---

Rerun analysis of cells before grafting with CC-regression.

### Load packages

``````{r}
#suppressMessages(library(scater))
#suppressMessages(library(SC3))
suppressMessages(require(gridExtra))
suppressMessages(library(Seurat))
``````


```{r}
load("../data/seurat_object_before.Rdata")

meta <- dataSA@meta.data
meta$SeuratCluster <- meta$res.0.6

``````

## Create Seurat Object

Create a new seurat object and normalize

```{r}
dataSA <- CreateSeuratObject(raw.data = dataSA@raw.data, min.cells = 3, min.genes = 200, project = "before_grafting",is.expr=1,meta.data=meta)

scale.factor <- mean(colSums(dataSA@raw.data))
dataSA <- NormalizeData(object = dataSA, normalization.method = "LogNormalize", scale.factor = scale.factor)

# variable genes
dataSA <- FindVariableGenes(object = dataSA, mean.function = ExpMean, dispersion.function = LogVMR, x.low.cutoff = 1, x.high.cutoff = 10, y.cutoff = 1,cex.text.use=0.2)
length(x = dataSA@var.genes)
```

## Cell cycle scoring

```{r}

### cell cycle genes
data(cc.genes)


# obs! genes only have gene symbol, in matrix we have gene name + EnsID
rn <- rownames(dataSA@raw.data)
gname <- unlist(lapply(strsplit(rn,":"), function(x) x[1]))
cc.genes <- lapply(lapply(cc.genes, match, gname), function(x) na.omit(rn[x]))
# one gene has no translation, MLF1IP, in our annotation has name CENPU
cc.genes$s.genes <- c(cc.genes$s.genes, rn[grep("CENPU", rn)])


dataSA <- CellCycleScoring(dataSA, g2m.genes = cc.genes$g2m.genes,
                          s.genes = cc.genes$s.genes)

table(dataSA@meta.data$Phase)
```

 
 
##  Cell cycle regression 

Regress out number of detected genes and cell cycle scores. Then run dim reduction and clustering.

```{r}
dataSA <- ScaleData(object = dataSA, vars.to.regress = c("nGene","S.Score","G2M.Score"),display.progress=F)

#PCA
dataSA <- RunPCA(object = dataSA, pc.genes = dataSA@var.genes, do.print = FALSE)

#Determine statistically significant principal components
dataSA <- JackStraw(object = dataSA, num.replicate = 100, display.progress=FALSE)
JackStrawPlot(object = dataSA, PCs = 1:20)

use.pcs <- c(1,2,4,5,7,9,10,12,13)  
dataSA <- FindClusters(object = dataSA, reduction.type = "pca", dims.use = use.pcs, 
resolution = 0.6, print.output = 0, save.SNN = TRUE)


#tSNE
dataSA <- RunTSNE(object = dataSA, dims.use = use.pcs, do.fast = TRUE)

```

## Plot

```{r}
### tSNE plots
TSNEPlot(object = dataSA)

# by sample_type
TSNEPlot(object = dataSA, group.by = "sample_type", colors.use = c( "hotpink1","grey56"))

### Clusters without Cell Cycle regression
TSNEPlot(object = dataSA, group.by = "SeuratCluster", colors.use = c("green","orange","cyan","yellow2","green4"))
```

```{r}
sessionInfo()

```