---
title: "Data_integration_wSS2"
output: 
  md_document:
    variant: markdown_github
---

Integration with the 3 rats using Seurat v3 data integration strategy. Also include the SS2 ES dataset at the same time. 

Scaling based on nFeature (number of detected genes) and percent.mito first for each object, and no scaling in integration step.

Also, change the resolution to get fewer clusters, so we do not have to merge clusters in the last step.

```{r packages, warning=FALSE}
suppressMessages(require(Seurat))
suppressMessages(require(Matrix))
suppressMessages(require(gridExtra))
suppressMessages(require(ggplot2))
suppressMessages(require(pheatmap))

```


### Load data

Load all the seurat objects per sample.

```{r load}
indir <- "../data/processed2/per_sample/"
rats <- c("rat11","rat39","rat45")

# load data
alldata <- list()
for (rat in rats){
  file.name <- paste(indir,"seurat_object_",rat,".Rdata", sep='')
  load(file.name)
  alldata[[rat]] <- ss
}

```  

### Load SS2 data

Read in rpkms from SS2 data, make seurat objects for ES and fetal derived grafted cells. 

```{r read.rpkm}
R <-read.table(gzfile("../data/ensembl_rpkms_filtered.csv.gz"), sep=",", header=T)

M <- read.table("../data/metadata_all_filtered.csv", sep=",", header=T)

# convert gene names to same format as in the 10x data
ss2.genes <- unlist(lapply(strsplit(rownames(R), ":"), function(x) x[1]))
ss2.genes <- make.unique(ss2.genes, sep= "-")
ds.genes <- rownames(alldata[[1]])

m <- match(ss2.genes, ds.genes)
m2 <- match(ds.genes, ss2.genes)
# only 21808 genes, out of 33526 in 10x data have a match.

# use instead ensembl ids?
ss2.ensembl <- unlist(lapply(strsplit(rownames(R), ":"), function(x) x[2]))
features <- read.table("../data/processed2/gene_annotation.tsv", header=T, sep="\t", quote = '')
ds.ensembl <- as.character(features[,1])
m3 <- match(ss2.ensembl, ds.ensembl)
m4 <- match(ds.ensembl, ss2.ensembl)
# then we have 30489 genes matching, use those!

# subset the features with only genes that are in the matrix (filtered out mt genes)
features <- features[match(ds.genes, features$unique_name),]
keep <- which(ss2.ensembl %in% as.character(features[,1]))

# subset the rpkm matrix with the same genes and change rownames
R <- R[keep,]
ss2.ensembl <- ss2.ensembl[keep]
trans <- as.character(features$unique_name[match(ss2.ensembl,as.character(features[,1]))])
rownames(R) <- trans

# take only the grafted cells.
es <- which(M$plate == "RC17_after_mesDA")
fetal <- which(M$plate == "fetal_after")

# add the clustering info from before
load("../../SC3/seurat_object_after.Rdata")
M.seurat <- dataS@meta.data

M.es <- M[es,]
M.es$Celltype <- as.character(M.seurat[match(rownames(M.es),rownames(M.seurat)),]$cluster)
M.es$res.0.6 <- M.seurat[match(rownames(M.es),rownames(M.seurat)),]$res.0.6


# create new seurat objects
alldata$ss2_es <- CreateSeuratObject(counts = R[,es], meta.data = M.es, project = "SS2_ES")

unlist(lapply(alldata,ncol))
```


Scale and normalize SS2 seurat objects.

```{r}
ss2 <- c("ss2_es")
verbose = FALSE
for (ss in ss2){
    alldata[[ss]] <- NormalizeData(object = alldata[[ss]], verbose = verbose)
    alldata[[ss]] <- FindVariableFeatures(object = alldata[[ss]], verbose = verbose )
    alldata[[ss]] <- ScaleData(object = alldata[[ss]], vars.to.regress = "nFeature_RNA", verbose = verbose )
}

```



## Do integration

Run for now with default settings. 



```{r integrate}

sel.pc <- 1:30
npcs <- 30

savefile <- "../data/processed2/integrated/seurat_integrated_rat_SS2_dimred_scale.Rdata"
data.wFetal <- alldata
alldata <- alldata[-4] #remove fetal

if (!file.exists(savefile)){
  data.anchors <- FindIntegrationAnchors(object.list = alldata, dims = sel.pc, scale=F)
  #rm(alldata)
  data.integrated <- IntegrateData(anchorset = data.anchors, dims = sel.pc)
  rm(data.anchors)
  DefaultAssay(object = data.integrated) <- "integrated"

  #Dimensionality reductions
  data.integrated <- ScaleData(object = data.integrated, verbose = FALSE)
  data.integrated <- RunPCA(object = data.integrated, npcs = npcs, verbose = FALSE)
  set.seed(1)
  data.integrated <- RunUMAP(object = data.integrated, reduction = "pca", dims = sel.pc)
  set.seed(1)
  data.integrated <- RunTSNE(object = data.integrated, reduction = "pca", dims = sel.pc)
  save(data.integrated, file=savefile)
}else{
  load(savefile)
  rm(alldata)
}
```

### Plot data

Plot as UMAP and tSNE embedding. 

Color by sample, or by celltype prediction from the individual clustering without integration.

```{r}
small.leg <- theme(legend.text = element_text(size=4), legend.key.size = unit(1,"point"))
DimPlot(object = data.integrated, reduction = "umap", group.by = "orig.ident") + NoAxes() + small.leg + ggtitle("UMAP")

DimPlot(object = data.integrated, reduction = "tsne", group.by = "orig.ident") + NoAxes() + small.leg + ggtitle("tSNE")

```

Some of the cells that were in the neuronal cluster in the 10X integration are now at one tip of the astro cluster with tSNE and an outlier group in UMAP.


Split cells by old clusters for SS2 cells. Clusters 0,1 are the 2 astrocyte clusters. Clusters 2,3 are the two FBLC clusters and cluster 5 is the neuronal cluster.

```{r}
DimPlot(object = data.integrated, reduction = "umap", group.by = "Celltype", split.by = "res.0.6") 

```

Seems to group the celltypes correctly.

### Plot marker genes

OBS! Before was in integrated space, now plot as RNA expression.

```{r}
data.rna <- data.integrated
data.rna@active.assay <- "RNA"

# plot some marker genes.
plot.genes <- c("TH","SLC6A3","SNAP25","GAP43", "NEFL","DLK1","OLIG1","GFAP","AQP4","COL1A1","DCN","FBLN1")
p1 <- FeaturePlot(data.rna, features = plot.genes, reduction = "tsne", pt.size = 0.2, combine = F, cols = c("yellow","red","black"))
p1 <- lapply(p1, function(x) x + NoAxes() + NoLegend())
grid.arrange(grobs=p1, ncol=4)

```
  
  
### Run clustering

```{r cluster}
# cluster
set.seed(1)
data.integrated <- FindNeighbors(object = data.integrated, dims = sel.pc, verbose = F)
data.integrated <- FindClusters(object = data.integrated, resolution = 0.1, verbose = F)

# plot clustering
DimPlot(data.integrated, reduction = "umap", label = T) + NoAxes()
DimPlot(data.integrated, reduction = "tsne", label = T) + NoAxes()

# split by sample
DimPlot(object = data.integrated, reduction = "umap", split.by = "Sample")

```

The "NA" sample is the SS2 cells. Seems like we have representation of most samples in most clusters. Cluster5 has few cells from rat11. Cluster 8 is mainly rat45 + SS2. 


Number of cells from each sample to each cluster:

```{r}
s <- split(data.integrated@active.ident,data.integrated@meta.data$orig.ident)
s <- lapply(s,table)
overlap <- Reduce(rbind,s)
rownames(overlap) <- names(s)


pheatmap(overlap, cluster_cols = F, cluster_rows = F, scale = "row", display_numbers = overlap, legend = F)
```


Number of cells per cluster

```{r}
table(data.integrated@active.ident)
```

### Check rat reads.

Add proportion rat reads to the metadata and plot onto tsne and as violins per cluster.

```{r}
# add in proportion rat reads into the meta data
samples <- unique(data.integrated@meta.data$Sample)
# remove ss2
samples <- samples[1:7]
data.integrated@meta.data$rat.ratio <- 0
data.integrated@meta.data$rat.umis <- 0


for (s in samples){
  sname <- gsub("-","_", s)
  rat.ratio <-  read.table(sprintf("../data/processed2/rat_filtering_%s.csv", sname), sep=",")
  rownames(rat.ratio) <- paste(s,rownames(rat.ratio), sep="_")
  rat.ratio <- rat.ratio[rownames(rat.ratio) %in% colnames(data.integrated),]
  data.integrated@meta.data$rat.ratio[match(rownames(rat.ratio),colnames(data.integrated))] <- rat.ratio$ratio
  data.integrated@meta.data$rat.umis[match(rownames(rat.ratio),colnames(data.integrated))] <- rat.ratio$rat_reads
}

FeaturePlot(data.integrated, features = c("rat.ratio","rat.umis"), reduction = "tsne")
VlnPlot(data.integrated, features = c("rat.ratio","rat.umis"), pt.size = 0.1)
```

Cluster 10 clearly stands out as having high proportion of rat reads, also cluster 11 have quite high values. But in total number of rat reads, cluster 9 & 11 is highest.

Same plots but removing SS2 data as we do not have the same stats there:

```{r}
keep <- colnames(data.integrated)[data.integrated@meta.data$orig.ident != "RC17"]
temp <- subset(data.integrated, cells = keep)

FeaturePlot(temp, features = c("rat.ratio","rat.umis"), reduction = "tsne")
VlnPlot(temp, features = c("rat.ratio","rat.umis"), pt.size = 0.1)

VlnPlot(temp, features = c("nFeature_RNA","nCount_RNA"), pt.size = 0.1)

rm(temp)

```

Clusters 7 & 10 clearly stands out as having few genes & few umis and that could be the reason why the proportion of rat reads are higher in those clusters.

Cluster 8 and cluster 11 (cycling) clearly have more genes and more UMIs. Could be related to development, where the more embryonic like neurons are bigger than the mature neurons. We saw the same in the mouse data. But it could also be related to the quality of the cells.


### Run DE detection

Run all tests with the normalized RNA data and plot as such.

```{r DE}
data.rna <- data.integrated
data.rna@active.assay <- "RNA"

printfile <- "../data/processed2/integrated/integrate_SS2_rat_marker_genes_scale_res0.1.txt"
force <- FALSE

  if (force | !file.exists(printfile)){
    print("running FindMarkers")
    markers <- FindAllMarkers(data.integrated, verbose = T, assay = "RNA")
    write.table(markers, file=printfile)
  }else {
    print(sprintf("reading file %s",printfile))
    markers <- read.table(printfile)
  }
```

Plot heatmap with top DE genes

```{r}
# Plot heatmap with top DE genes
  per.cluster <- split(markers, markers$cluster)
  top10 <- lapply(per.cluster, function(x) x$gene[x$avg_logFC>0][1:10])
  top10 <- unique(na.omit(unlist(top10)))
  plotgenes <- list()
  plotgenes[[1]]<-top10
  nPlot <- 50
  if (length(top10) > nPlot){
    # plot 60 per page
    splitN <- ceiling(length(top10)/nPlot)
    plotgenes <- split(top10, cut_number(1:length(top10), splitN))
  }
  for (i in 1:length(plotgenes)){
    print(DoHeatmap(data.rna, features = plotgenes[[i]], slot="data"))
  }

```


Plot top DE genes onto UMAP.

```{r plot.de}
top8 <- lapply(per.cluster, function(x) as.character(x$gene[x$avg_logFC>0][1:8]))
plots <- list()

for (cl in names(top8)){
    cc <- colnames(data.integrated)[data.integrated@active.ident == cl]
    p0 <- DimPlot(data.rna, reduction = "umap", pt.size = 0.1, cells.highlight = cc)  + NoAxes() + NoLegend() + ggtitle(sprintf("cluster %s",cl)) + theme(plot.title = element_text(size=6),  plot.margin = rep(unit(0,"null"),4) , panel.spacing = unit(0,"null"))
    p1 <- FeaturePlot(data.rna, features = top8[[cl]], pt.size = 0.1, reduction = "umap", combine = F, cols = c("yellow","red","black"))
    p1 <- lapply(p1, function(x) x + NoAxes() + NoLegend() + theme(plot.title = element_text(size=6),plot.margin = rep(unit(0,"null"),4) , panel.spacing = unit(0,"null")))
    p1$cl <- p0
    p1 <- p1[c(9,1:8)]
    plots <- append(plots,p1)
}

nPage <- ceiling(length(top8)/6)
for (p in 1:nPage){
    idx <- (p*54-53):min(p*54,length(top8)*9)
    grid.arrange(grobs = plots[idx], ncol=9, nrow=6)
}

```


### New celltype prediction

Based on new integrated clusters. 

```{r celltype}
overlap_phyper2<-function(L1,L2,bg=length(unique(c(unlist(L1),unlist(L2))))){
   # takes two list with indices and creates a matrix with pvalue for overlap between elements
   # phyper test uses all entries in L as background if bg is not specified.
   nL1<-length(L1)
   nL2<-length(L2)
   M<-mat.or.vec(nL1,nL2)
   P<-mat.or.vec(nL1,nL2)
   P[,]<-1
   for (i in 1:nL1){
      for (j in  1:nL2){
        M[i,j]<-length(intersect(L1[[i]],L2[[j]]))
        if (length(L1[[i]])==0 | length(L2[[j]])==0 ) {
          P[i,j] <- 1
        }else{
          P[i,j]<-1-phyper(M[i,j],length(L1[[i]]),bg-length(L1[[i]]),length(L2[[j]]))
        }
      }
   }
   colnames(P)<-names(L2)
   rownames(P)<-names(L1)
   colnames(M)<-names(L2)
   rownames(M)<-names(L1)   
   
   return(list(P=P,M=M))
}

# read panglaoDB file
pd <- read.table("/Users/asbj/local/projects/sc-devop/celltyping/data/PanglaoDB_all_cells_190215.txt", sep="\t", header=T, quote='')
pd.sets <- split(as.vector(pd$official.gene.symbol), pd$cell.type)

  # split genes by cluster
  s <- split(markers, markers$cluster)
  sig.up <- lapply(s, function(x) as.vector(x[x$avg_logFC>0 & x$p_val_adj<0.01,]$gene))

  # background is all genes expressed
  rs <- rowSums(data.integrated@assays$RNA@data)

  bg <- sum(rs > 0)

  ph <- overlap_phyper2(pd.sets, sig.up, bg=bg)$P

  # select top 3 celltypes per cluster to plot
  nTop = 3
  topG <- unique(as.vector(apply(ph, 2, function(x) order(x)[1:nTop])))
  selected <- ph[topG,]

  pheatmap(-log10(selected+1e-17))


  # assign a label to each cluster by its top scoring celltype
  top.ct <- apply(selected,2,which.min)
  assigned <- rownames(selected)[top.ct]
  # if p-value > 0.1 set as NA
  assigned[apply(selected,2,min)>0.1] <- NA

  names(assigned) <- colnames(selected)
  data.integrated <- AddMetaData(data.integrated, assigned[as.character(data.integrated@active.ident)], col.name="CelltypeI")
  print(DimPlot(object = data.integrated, reduction = "tsne", group.by = "CelltypeI"))
  print(DimPlot(object = data.integrated, reduction = "umap", group.by = "CelltypeI"))

  
```



### Clustering overlap

Compare to clustering with the individual datasets.

```{r}
cl.before  <- data.integrated@meta.data$RNA_snn_res.0.6
sample.def <- data.integrated@meta.data$orig.ident
cl.def <- paste(sample.def,cl.before, sep="_cl")

data.integrated <- AddMetaData(data.integrated, cl.def, col.name="IndividualClusters")

# Cluster overlap
l1 <- split(1:ncol(data.integrated),data.integrated@meta.data$integrated_snn_res.0.1)
l2 <- split(1:ncol(data.integrated), cl.def)
o <- overlap_phyper2(l1,l2)

pheatmap(-log10(o$P+1e-16), cluster_rows = F, cluster_cols = F, display_numbers = o$M)

# and count total number of cells in each cluster
table(data.integrated@active.ident)

```
  
The 2 clear neuronal clusters (cluster9 & cluster10), have 174 and 57 cells, of which 35 are SS2 (all in cluster 9).

Before (without SS2 data) it was 139 + 58 cells in the two neuron clusters (8 & 10), so 1 cell have moved from neuronal cluster to another cluster.
  
### Save data  
  
```{r}
save(data.integrated, file = "../data/processed2/integrated/seurat_integrated_rat_SS2_scale_res0.1.Rdata")

```
  


Compare SS2 clusters to current clusters:

```{r}
new <- data.integrated
m <- new@meta.data[new@meta.data$orig.ident == "RC17",]
ct2 <- Reduce(cbind,lapply(split(factor(m$Celltype), m$integrated_snn_res.0.1), table))
colnames(ct2) <- levels(m$integrated_snn_res.0.1)

pheatmap(ct2, cluster_rows = F, cluster_cols = F, display_numbers = ct2, fontsize_number = 10)
```
  

For the SS2 data, the neuronal cluster is identical, but there are some cells that have changed cluster for the FBLCs and the Astrocytes. 


# Compare to mouse brain atlas

Read in the mouse brain atlas data and get a list of marker genes to calculate correlations on.

```{r atlas_data, warning=FALSE}
suppressMessages(library(loomR))
# to load loomR - need to first unload ‘dplyr’, ‘httr’?

lfile <- connect(filename = "../../data/linnarsson_atlas/l5_all.agg.loom", mode = "r", skip.validate = T)

exprs <- lfile[["matrix"]][,]
exprs <- t(exprs)

names <- lfile[["col_attrs"]]$names
clust <- lfile[["col_attrs/ClusterName"]][]
colnames(exprs) <- clust

gene.names <- lfile[["row_attrs/Gene"]][]
rownames(exprs) <- gene.names

# attr.df <- lfile$get.attribute.df(MARGIN = 2, attribute.names = names)
# does not work to run get.attribute, 
#  An object with name col_attrs/cell_names does not exist in this group

M <- list()
for (n in names){
  M[[n]] <- lfile[["col_attrs"]][[n]][]
}
M <- Reduce(cbind,M)
rownames(M) <- clust
colnames(M) <- names
M <- data.frame(M)

# extract all their marker genes
markersA <- unique(unlist(sapply(as.vector(M$MarkerGenes), strsplit, " ")))
#length(markersA)

# and our marker genes
markers2 <- unique(markers[markers$p_val_adj<0.001,"gene"])
#length(markers2)
```

Translate human to mouse genes.

```{r, orthologs}
transfile <- "../data/processed2/linnarsson_atlas/human_gene_translations.txt"

# get ensembl ids for the human genes
gene.info <- read.table("../data/processed2/gene_annotation.tsv", sep="\t", quote='', header=T)
human.ensembl <- gene.info$ensembl_gene_id

if (file.exists(transfile)){
  gene.translation <- read.table(transfile)
}else{

  library(biomaRt)
  # Load human ensembl attributes
  #human = biomaRt::useMart("ensembl", dataset = "hsapiens_gene_ensembl")
  human <- useMart(host="uswest.ensembl.org", "ENSEMBL_MART_ENSEMBL", dataset="hsapiens_gene_ensembl")
  # Load mouse ensembl attributes
  #mouse = biomaRt::useMart("ensembl", dataset = "mmusculus_gene_ensembl")
  mouse <- useMart(host="uswest.ensembl.org", "ENSEMBL_MART_ENSEMBL", dataset="mmusculus_gene_ensembl")
  
  # Link both datasets and retrieve human gene id + name
  gene.translation = biomaRt::getLDS(attributes = c("external_gene_name","ensembl_gene_id"), filters = "ensembl_gene_id", values = human.ensembl , mart = human, attributesL = c("ensembl_gene_id","external_gene_name"), martL = mouse, uniqueRows = T)

  #head(gene.translation)
  
  # only keep genes that also exists in the expression data
  matches1 <- sapply(gene.translation$Gene.name, match, rownames(data.integrated@assays$RNA@counts))
  matches2 <- sapply(gene.translation$Gene.name.1, match, rownames(exprs))
  keep <- (is.na(matches1) + is.na(matches2) )==0
  gene.translation <- gene.translation[keep,]
    
  write.table(gene.translation, file=transfile)
}

# select only genes that are expressed in 10 cells our data
nE <- rowSums(data.integrated@assays$RNA@counts > 0)
expressed.genes <- rownames(data.integrated@assays$RNA@counts)[nE>10]
gene.translation <- gene.translation[gene.translation$Gene.name %in% expressed.genes,]

# select only genes that are among the marker genes
keep.markersA <- which(gene.translation$Gene.name.1 %in% markersA)
keep.markers2 <- which(gene.translation$Gene.name %in% markers2)
print("our markers:")
length(keep.markers2)
print("atlas markers:")
length(keep.markersA)
print("in both:")
length(intersect(keep.markers2,keep.markersA))
keep.markers <- union(keep.markersA,keep.markers2)
print("total markers:")
length(keep.markers)
# only 201 genes as markers in both datasets.
gene.translation <- gene.translation[keep.markers,]
```

Calculate mean expression across the markers for our data. And fetch mean expression for the same markers in the atlas data.

```{r}
# use the norm.data slot.
exprR <- data.integrated@assays$RNA@data
exprR <- exprR[gene.translation$Gene.name,]

clust2cell <- split(1:ncol(data.integrated), data.integrated@active.ident)
exprsC <- Reduce(cbind,lapply(clust2cell, function(x) rowMeans(exprR[,x])))
colnames(exprsC) <- names(clust2cell)

exprsA <- log2(exprs[match(gene.translation$Gene.name.1, rownames(exprs)),]+1)
```

Calculate correlations

```{r, fig.width=10, fig.height=6}
cC <- cor(exprsC,exprsA, method = "spearman")

include.annot <- c("TaxonomyRank1","TaxonomyRank2","TaxonomyRank3","TaxonomyRank4")
colorsC <- M[,include.annot]
  
# keep order for atlas cells by their Taxonomy ranks
o <- order(M$TaxonomyRank1, M$TaxonomyRank2, M$TaxonomyRank3)
pheatmap(cC[,o], annotation_col = colorsC[,1:3], cluster_cols = F, show_colnames = F, fontsize = 6) 
```

Top correlation per cluster, print top 6 correlating atlas clusters.

```{r}
# top correlation per group are clusters:
for(c in rownames(cC)){
  print(c)
  print(head(sort(cC[c,],decreasing = T)))
}
```

Clusters 9,10 - clearly neuronal. Closest hits are HYPEP4 & 5, hypothalamus neurons.

### Linnarsson data at tax level 4
Calculate mean expression at level 4 and compare to our clusters.

```{r, fig.width=10, fig.height=6}
level4 <- split(1:ncol(exprsA), M$TaxonomyRank4)
get.mean <- function(x){
  if (length(x) == 1) { return(exprsA[,x])}
  else { return(rowMeans(exprsA[,x]))}
}
mean.level4 <- lapply(level4, get.mean)
exprs4 <- Reduce(cbind, mean.level4)
colnames(exprs4) <- names(level4)

#make color def for Tax rank2 
tax2 <- as.character(M[match(names(level4), M$TaxonomyRank4),]$TaxonomyRank2)
colorsC <- data.frame(TaxonomyRank2 =  tax2)
rownames(colorsC) <- names(level4)

c4S <- cor(exprsC,exprs4, method = "spearman")
pheatmap(c4S, fotsize_col = 8, annotation_col = colorsC)
```

Take top correlating brain atlas cluster and predict celltype for our clusters.

```{r}
#for(c in rownames(c4S)){
#  print(c)
#  print(head(sort(c4S[c,],decreasing = T),3))
#}


new.annot <- colnames(c4S)[apply(c4S, 1,which.max)]
names(new.annot) <- rownames(c4S)
new@meta.data$CelltypeMBA <- new.annot[new@active.ident]
print(new.annot)

DimPlot(new, group.by = "CelltypeMBA", label = T) + NoAxes() + NoLegend()
```

### Make a plot with only the Enteric glia subclusters

```{r, fig.width=10, fig.height=6}
enteric <- grep("Enteric glia", M$TaxonomyRank4)
cE <- cor(exprsC,exprsA[,enteric], method = "spearman")
pheatmap(cE)
```

# Proportion cells from different sortings

Visualize per cluster:

* Number of cells from each rat
* Number of cells from different sortings

And opposite, for each rat - visualize how the cells are distributed to different clusters.

In all plots - "NA" is SS2 data.

```{r}
meta <- new@meta.data

ggplot(meta, aes(x=integrated_snn_res.0.1,fill=Rat)) + geom_bar()
ggplot(meta, aes(x=integrated_snn_res.0.1,fill=Rat)) + geom_bar(position = "fill") 
ggplot(meta, aes(x=integrated_snn_res.0.1,fill=Type)) + geom_bar(position = "fill") 

# per rat instaed.
ggplot(meta, aes(x=Rat, fill=integrated_snn_res.0.1)) + geom_bar()
ggplot(meta, aes(x=Rat, fill=integrated_snn_res.0.1)) + geom_bar(position = "fill") 

```


```{r}
sessionInfo()
```