---
title: "Manuscript figures w/o SS2"
output: 
  md_document:
    variant: markdown_github
---

Plot figures for manuscript. Use the integrated object from Data_integration.Rmd 
(file seurat_integrated_rat_scale_res0.1.Rdata)

Plot UMAP with:

* Clusters (4 main celltypes)
* FACS/NotFACS
* SS2/10x

Violin plots for the 4 clusters - same markers as in SS2 data only.


```{r packages, warning=FALSE}
suppressMessages(require(Seurat))
suppressMessages(require(Matrix))
suppressMessages(require(gridExtra))
suppressMessages(require(ggplot2))
suppressMessages(require(pheatmap))

```

```{r load}
load(file = "../data/processed2/integrated/seurat_integrated_rat_scale_res0.1.Rdata")

# reassing cluster names to celltypes
celltypes <- c("Astrocyte","FBLC","Neuron","Cycling")
names(celltypes) <- as.character(0:3)

ct <- celltypes[data.integrated@active.ident]
data.integrated <- AddMetaData(data.integrated, ct, col.name = "CelltypeCluster")
```

### plot UMAPs

```{r umap}
# make one version with labels in plot
scaleC <- scale_colour_manual(values = c("blue1", "gray","green3", "red1"))

# Per cluster with legend
p1 <- DimPlot(data.integrated, group.by = "CelltypeCluster") + NoAxes() +scaleC

# one with FACS/notFACS
p2 <- DimPlot(data.integrated, group.by = "Type", order = c("NotFACS","FACS")) + NoAxes() + scale_colour_manual(values = c("cyan", "magenta"))

# one with Rat
p3 <- DimPlot(data.integrated, group.by = "Rat") + NoAxes()

pdf("../data/figures2/umap_integrated_woSS2.pdf")
grid.arrange(p1,p2,p3, ncol=2)

# all same plots without legends.
p1 <- DimPlot(data.integrated, group.by = "CelltypeCluster") + NoAxes() + 
  scaleC + NoLegend() + ggtitle("Clusters")
p2 <- DimPlot(data.integrated, group.by = "Type", order = c("NotFACS","FACS")) + NoAxes() + NoLegend() + 
  scale_colour_manual(values = c("cyan", "magenta")) + ggtitle("FACS type")
p3 <- DimPlot(data.integrated, group.by = "Rat") + NoAxes() + NoLegend() +  ggtitle("Rat")
grid.arrange(p1,p2,p3, ncol=2)
dev.off()
```



### gene violin plots as in SS2 figure.

```{r violin}
genes <- list()
genes$Astrocyte <-  c("AQP4", "GFAP", "SLC1A3",  "GJA1", "EDNRB", "SLC4A4")
genes$Oligodentrocyte <- c("OLIG1", "OLIG2","NKX2-2",  "SOX10",  "PLP1",  "PMP2")
genes$PanNeuronal <- c("GAP43", "RBFOX3","NSG2","SNAP25", "NEFL", "SYN1")
genes$DopamineNeuron <-c("TH","NR4A2","SLC18A2", "DDC",  "RET", "GFRA1")
genes$FBLC <- c("PDGFRA",   "COL1A1",  "COL1A2",  "LUM",     "DCN",     "FBLN1")

temp <- data.frame(t(data.integrated@assays$RNA@data[unlist(genes),]), check.names = F)
temp$cluster <- data.integrated@meta.data$CelltypeCluster
short <- temp$cluster
short[short=="Cycling"] <- "CC"
short[short=="Neuron"] <- "N"
short[short=="Astrocyte"] <- "AC"
temp$cluster <- short

pl <- list()
noleg <- theme(legend.position="none")
scaleF <- scale_fill_manual(values = c("blue1", "gray","green3", "red1"))
for (gene in unlist(genes)){
  pl[[gene]] <- ggplot() + geom_violin(data=temp,aes_(x=as.name("cluster"),y=as.name(gene),fill=as.name("cluster"), colour = as.name("cluster") ), scale="width") + 
    theme_void() + noleg + scaleF + scaleC + theme(title =element_text(size=6, face='bold')) + ggtitle(gene)
}

# OBS! to get it filled by row instead of column, rearrange the plots
pl2 <- pl[as.vector(t(matrix(names(pl),nrow=6)))]

pdf("../data/figures2/violins_integrated_woSS2.pdf", width = 14, height = 7)
grid.arrange(grobs=pl2, nrow=6)
dev.off()

```


### Umap plots of gene list 

Gene list from Katarina with genes (gene_list_NatureMedicine.csv)

```{r}
genes2 <- read.table("../data/figures2/gene_list_NatureMedicine.csv", header = T)

genes2$symbol <- unlist(lapply(strsplit(as.character(genes2$Gene),":"), function(x) x[1]))

# is all the same genes as above except 5
# [1] "PCDH15"  "SLC17A6" "SLC17A8" "GAD2"    "SLC32A1"
m <- match(genes2$symbol, unlist(genes))
genes2[which(is.na(m)),"symbol"]

data.integrated@active.assay <- "RNA"
plots <- FeaturePlot(data.integrated, features = genes2$symbol, reduction = "umap", combine=F, cols = c("yellow","red","black"))
plots <- lapply(plots, function(x) x + NoAxes() + theme(legend.text = element_text(size=6)))

pdf("../data/figures2/umap_gene_plots_woSS2.pdf", width = 10, height = 7)
for (i in 1:4){
  sel <- (i*9-8):min(i*9,length(plots))
  grid.arrange(grobs=plots[sel])
}
dev.off()

```


```{r}
sessionInfo()
```
